Additional Tables

### 2019-05-22 notebooks/Clustering analysis.Rmd
added tables and minor fixes

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggtree)
library(cluster)
library(Biostrings)
library(ape)
library(tibble)
library(cowplot)
library(knitr)
library(vegan)
library(distanceR)
```

@@

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% ex_samples)

@@

cgMLST_allele_data <- read.table("../data/chewbbaca/complete_results/cgMLST.tsv",
                              sep = "\t",
                              header = TRUE,
                              stringsAsFactors = FALSE) %>%
  mutate(FILE = sub("_pilon_spades.fasta", "", FILE)) %>%
  dplyr::rename("ref" = FILE) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref) %>%
  filter(id %not_in% ex_samples)

>>>>

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggtree)
library(cluster)
library(Biostrings)
library(ape)
library(tibble)
library(knitr)
library(vegan)
library(distanceR)
```

@@

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)
  filter(id %not_in% ex_samples)

@@

cgMLST_allele_data <- read.table("../data/chewbbaca/complete_results/cgMLST.tsv",
                              sep = "\t",
                              header = TRUE,
                              stringsAsFactors = FALSE) %>%
  mutate(FILE = sub("_pilon_spades.fasta", "", FILE)) %>%
  dplyr::rename("ref" = FILE) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref) %>%
  filter(id %not_in% ex_samples)
```

### 2019-05-22 notebooks/article_notebook2.Rmd
added tables and minor fixes

>>>>

# R and R-Packages
R version 3.6.0 [1] was used in the present study. The following packages were used:

| Package       | Version | Reference |
|---------------|---------|-----------|
| dplyr         | 0.8.0.1 |   [2]     |
| tidyr         | 0.8.3   |   [3]     |
| ggplot2       | 3.1.1   |   [4]     |
| purrr         | 0.3.2   |   [5]     |
| tibble        | 2.1.1   |   [6]     |
| Biostrings    | 2.50.2  |   [7]     |
| vegan         | 2.5.4   |   [8]     |
| stringr       | 1.4.0   |   [9]     |
| cluster       | 2.0.8   |   [10]    |
| ape           | 5.3     |   [11]    |
| ggtree        | 1.14.6  |   [12]    |
| RColorBrewer  | 1.1-2   |   [13]    |
| cowplot       | 0.9.4   |   [14]    |
| knitr         | 1.22    |   [15]    |
| kableExtra    | 1.1.0   |   [16]    |
| ggsci         | 2.9     |   [17]    |
| fastqcr       | 0.1.2   |   [18]    |
| scales        | 1.0.0   |   [19]    |
| viridis       | 0.5.1   |   [20]    |

# References
[1] RCoreTeam. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/. 2018.

[2] Wickham H, François R, Henry L, Müller K. dplyr: A Grammar of Data Manipulation [Internet]. 2019. Available from: https://cran.r-project.org/package=dplyr

[3] Wickham H, Henry L. tidyr: Easily Tidy Data with “spread()” and “gather()” Functions [Internet]. 2019. Available from: https://cran.r-project.org/package=tidyr

[4] Wickham H, Chang W, Henry L, Pedersen TL, Takahashi K, Wilke C, et al. ggplot2: Create Elegant Data Visualisations Using the Grammar of Graphics [Internet]. 2019. Available from: https://cran.r-project.org/package=ggplot2

[5] Henry L, Wickham H. purrr: Functional Programming Tools [Internet]. 2019. Available from: https://cran.r-project.org/package=purrr

[6] Müller K, Wickham H. tibble: Simple Data Frames [Internet]. 2019. Available from: https://cran.r-project.org/package=tibble

[7] Pagès H, Aboyoun P, Gentleman R, DebRoy S. Biostrings: Efficient manipulation of biological strings. 2019.

[8] Oksanen J, Blanchet FG, Friendly M, Kindt R, Legendre P, McGlinn D, et al. vegan: Community Ecology Package [Internet]. 2019. Available from: https://cran.r-project.org/package=vegan

[9] Wickham H. stringr: Simple, Consistent Wrappers for Common String Operations [Internet]. 2019. Available from: https://cran.r-project.org/package=stringr

[10] Maechler M, Rousseeuw P, Struyf A, Hubert M. cluster: “Finding Groups in Data”: Cluster Analysis Extended Rousseeuw et al. [Internet]. 2019. Available from: https://cran.r-project.org/package=cluster

[11] Paradis E, Blomberg S, Bolker B, Brown J, Claude J, Cuong HS, et al. ape: Analyses of Phylogenetics and Evolution [Internet]. 2019. Available from: https://cran.r-project.org/package=ape

[12] Yu G, Smith DK, Zhu H, Guan Y, Lam TT-Y. Ggtree: a package for visualization and annotation of phylogenetic trees with their covariates and other associated data. McInerny G, editor. Methods Ecol Evol [Internet]. 2017 Jan;8(1):28–36. Available from: http://doi.wiley.com/10.1111/2041-210X.12628

[13] Neuwirth E. RColorBrewer: ColorBrewer Palettes [Internet]. 2014. Available from: https://cran.r-project.org/package=RColorBrewer

[14] Wilke CO. cowplot: Streamlined Plot Theme and Plot Annotations for “ggplot2” [Internet]. 2019. Available from: https://cran.r-project.org/package=cowplot

[15] Xie Y. knitr: A General-Purpose Package for Dynamic Report Generation in R [Internet]. 2019. Available from: https://cran.r-project.org/package=knitr

[16] Zhu H. kableExtra: Construct Complex Table with “kable” and Pipe Syntax [Internet]. 2019. Available from: https://cran.r-project.org/package=kableExtra

[17] Xiao N. ggsci: Scientific Journal and Sci-Fi Themed Color Palettes for “ggplot2” [Internet]. 2018. Available from: https://cran.r-project.org/package=ggsci

[18] Kassambara A. fastqcr: Quality Control of Sequencing Data [Internet]. 2019. Available from: https://cran.r-project.org/package=fastqcr

[19] Wickham H. scales: Scale Functions for Visualization [Internet]. 2018. Available from: https://cran.r-project.org/package=scales

[20] Garnier S. viridis: Default Color Maps from “matplotlib” [Internet]. 2018. Available from: https://cran.r-project.org/package=viridis
